### 2016-03-31 thesis/conclusions.tex
back from gramps

we do not consider possible for current automatic routines to reproduce our human-supervised analysis. \\

@@

sequence than previously reported \citep{grahamscott2013}. 

@@

>>>>

we do not consider it possible for current automatic routines to reproduce our human-supervised analysis. \\

@@

sequence (with a log-slope of $1.53 \pm 0.20$) than previously reported ($2.73 \pm 0.55$, \citealt{grahamscott2013}). 

@@

However, this might be due to our sample selection and this result might change once reasonable number of galaxies 
with low-mass black holes ($M_{\rm BH} \lesssim 10^6 \rm~M_\odot$) will be added to the $M_{\rm BH} - L_{\rm sph}$ diagram 
(see Ciambur et al.~\emph{in preparation}).
